A comparative analysis of penalized linear mixed models in structured genetic data

### 2020-09-21 main.tex
3.6.2 edits

\pb{Vanderwas citation: https://doi.org/10.1186/s12890-015-0040-0}

We generated these synthetic phenotypes using three types of high-dimensional ($p > n$) $\bG$ matrices, which were then standardized to yield the corresponding $\bX$ matrix: (1) simulated SNP data from admixed subpopulations, (2) simulated SNP data from independent subpopulations, and (3) real genome-wide SNP data from known caucasian ($n = 417$), African American ($n = 134$), and Hispanic ($n = 37$) subpopulations \anna{cite Vanderwas data PATRICK TO DO}. We refer to these as the 1D Linear Admixture, Independent Subpopulations, and Empirical data, respectively. For all data types $p = 1000$ with 50 causal SNPs. For the simulated 1D Linear Admixture and Independent Subpopulations data $n = \{200, 400, 600, 800 \}$, and $n = 588$ for the Empirical data.

>>>>

We generated these synthetic phenotypes using three types of high-dimensional ($p > n$) $\bG$ matrices, which were then standardized to yield the corresponding $\bX$ matrix: (1) simulated SNP data from admixed subpopulations, (2) simulated SNP data from independent subpopulations, and (3) real genome-wide SNP data from known caucasian ($n = 417$), African American ($n = 134$), and Hispanic ($n = 37$) subpopulations \citep{larkin2015objectives}. We refer to these as the 1D Linear Admixture, Independent Subpopulations, and Empirical data, respectively. For all data types $p = 1000$ with 50 causal SNPs. For the simulated 1D Linear Admixture and Independent Subpopulations data $n = \{200, 400, 600, 800 \}$, and $n = 588$ for the Empirical data.
